Bullet Data Preparation for LIME Diagnostics Paper

### 2020-09-23 code/02-data-preparation.Rmd
fixed hyperlink

The code below removes observations based on Eric Hare's code (available [here](ttps://github.com/erichare/imaging-paper/blob/master/code/full_run.R)), which he thinks may be the code used to train `rtrees`:

>>>>

The code below removes observations based on Eric Hare's code (available [here](https://github.com/erichare/imaging-paper/blob/master/code/full_run.R)), which he thinks may be the code used to train `rtrees`:
